\documentclass[a4paper, 11pt]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}
\nopagenumbers{}

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\recomputelengths

\firstname{Shen}
\familyname{Fu}
\address{No. 373, Huangshan Rd., Shushan District}{Hefei, Anhui Province, China 230022}
\phone{(+86)~157~7969~2697}
\email{sh.fu@outlook.com}
\homepage{fr4nk1in-ustc.github.io}

\begin{document}
\makecvtitle

\section{Education}
\cventry{2020~--~2024 (expected)}{B.E. in Computer Science and Technology}{University of Science and Technology of China}{China}{}{
    \begin{itemize}
        \item School of the Gifted Young
        \item \textbf{Major GPA: 4.05/4.30}, Cumulative GPA: 3.89/4.30, Rank: 24/262
        \item Relevant coursework:
              \begin{itemize}
                  \item Data Structure (92)
                  \item Operating System (90)
                  \item Computer Organization (91)
                  \item Algorithm
                  \item Computer Network
                  \item Compiler
              \end{itemize}
    \end{itemize}
}

\section{Projects}
\cventry{May 2022}{RISC-V Sub}{Self-Designed CPU Core}{}{}{
    \begin{itemize}
        \item A 32-bit RISC-V ISA CPU core with 5-stage pipeline and 2-bit
              dynamic branch prediction, implemented in Verilog.
        \item Supports a subset of RV32I instructions, including arithmetic,
              logical, memory, and control instructions.
        \item Successfully demonstrated the design by running on FPGA.
        \item Independently developed and integrated the core with a Processor
              Debug Unit (PDU).
    \end{itemize}
}

\cventry{Jan 2023}{CminusF Compiler}{Compiler for C-Minus-F (subset of C)}{}{}{
    \begin{itemize}
        \item Utilized a simplified version of LLVM IR called LightIR.
        \item Implemented the front-end parser, the IR generation and some
              optimizations.
        \item Implemented a GVN analysis to eliminate redundant code and
              propagate constant values.
        \item Generated machine code via LLVM's backend.
    \end{itemize}
}

\section{Awards and Scholarships}

\cvitem{Dec 2020}{Outstanding Freshman Scholarship (Grade 2)}
\cvitem{Jan 2022}{Chen Linyi Scholarship}
\cvitem{Jan 2023}{Jianghuai \& NIO Automobile Scholarship}

\section{Skills}
\subsection{Programming Languages}
\cvitem{Skilled}{C/C++, Python, Verilog, Markdown, \LaTeX}
\cvitem{Familiar}{Lua, Shell Script}

\subsection{Tools and Operating Systems}
\cvitem{Experienced}{Git, Vim, Docker}
\cvitem{Familiar}{Linux, Windows}

\subsection{Languages}
\cvitem{Native}{Mandarin Chinese}
\cvitem{Fluent}{English}

\end{document}
